Actuator line modeling of vertical-axis turbines

### 2016-04-29 paper.tex
Periods inside captions and make figs smaller to save space

    \includegraphics[width=0.85\textwidth]{RVAT-ALM_verification}

@@

    \includegraphics[width=0.85\textwidth]{RM2-ALM_verification}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM_perf-curves}

@@

    \includegraphics[width=0.9\textwidth]{RVAT-ALM_meancontquiv}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM_kcont}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM_wake-profiles}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM_recovery-bar-chart}

@@

    \includegraphics[width=0.85\textwidth]{RM2-ALM_perf-curves}

@@

    \includegraphics[width=0.9\textwidth]{RM2-ALM_meancontquiv}

@@

    \includegraphics[width=0.9\textwidth]{RM2-ALM_kcont}

@@

    \includegraphics[width=0.85\textwidth]{RM2-ALM_wake-profiles}

@@

    \includegraphics[width=0.85\textwidth]{RM2-ALM_recovery-bar-chart}

    \caption{Weighted average momentum recovery terms at $x/D=0.93$ for the RM2
        actuator line model with a $k$--$\epsilon$ RANS closure and the experiments
        described in Chapter~\ref{chap:RM2}}.

@@

    \includegraphics[width=\textwidth]{RVAT-ALM-LES_vorticity-snapshot}

@@

    \includegraphics[width=0.9\textwidth]{RVAT-ALM-LES_meancontquiv}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM-LES_kcont}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM-LES_wake-profiles}

@@

    \includegraphics[width=0.85\textwidth]{RVAT-ALM-LES_recovery-bar-chart}

    \caption{Weighted average momentum recovery terms at $x/D=1$ for the RVAT
        ALM LES using the Smagorinsky SGS model}.

>>>>

    \includegraphics[width=0.7\textwidth]{RVAT-ALM_verification}

@@

    \includegraphics[width=0.7\textwidth]{RM2-ALM_verification}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM_perf-curves}

@@

    \includegraphics[width=0.75\textwidth]{RVAT-ALM_meancontquiv}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM_kcont}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM_wake-profiles}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM_recovery-bar-chart}

@@

    \includegraphics[width=0.7\textwidth]{RM2-ALM_perf-curves}

@@

    \includegraphics[width=0.75\textwidth]{RM2-ALM_meancontquiv}

@@

    \includegraphics[width=0.7\textwidth]{RM2-ALM_kcont}

@@

    \includegraphics[width=0.7\textwidth]{RM2-ALM_wake-profiles}

@@

    \includegraphics[width=0.7\textwidth]{RM2-ALM_recovery-bar-chart}

    \caption{Weighted average momentum recovery terms at $x/D=0.93$ for the RM2
        actuator line model with a $k$--$\epsilon$ RANS closure and the experiments
        described in Chapter~\ref{chap:RM2}.}

@@

    \includegraphics[width=0.8\textwidth]{RVAT-ALM-LES_vorticity-snapshot}

@@

    \includegraphics[width=0.75\textwidth]{RVAT-ALM-LES_meancontquiv}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM-LES_kcont}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM-LES_wake-profiles}

@@

    \includegraphics[width=0.7\textwidth]{RVAT-ALM-LES_recovery-bar-chart}

    \caption{Weighted average momentum recovery terms at $x/D=1$ for the RVAT
        ALM LES using the Smagorinsky SGS model.}
